Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2018-06-15 paper.tex
Update survival prob figs to use V_osc instead of H_nunu

We also solve for the flavor evolution of this system,
integrating $S$ according to Eqn.~\ref{eqn:schroedinger},
as described in \cite{zhu2016-mnr_nsns_remnant}.
We show the survival probabilities for $\nu_e$ and $\bar{\nu}_e$
for the \emph{noscat} treatment in Fig.~\ref{fig:survival-noscat},
and for the \emph{scat} treatment in Fig.~\ref{fig:survival-scat}.
The survival probability is the probability that a neutrino, if measured,
will be found to be in its original flavor state.
The survival probabilities are computed at each point along the trajectory
from the absolute square of the diagonal terms of the flavor evolution matrix,
$P_{\nu_\alpha \to \nu_\alpha} = |S_{\alpha \alpha}|^2$.
When $P_{\nu_e \to \nu_e}$ decreases,
as can be seen for example in Fig.~\ref{fig:survival-scat} for $r>400$~km,
some of the $e$ neutrinos have oscillated into $\mu$ or $\tau$ neutrinos.

@@

\begin{figure}
  \resizebox{\columnwidth}{!}{\input{fig-survival_prob-noscat_ih.tex}}
  % Flavor evolution by Yonglin, see emails 5.9.18, 5.16.18
  % Data: $DIR/300-1499kmACC12Step2NE30IH051418m12sc.dat2p
  % Script: $DIR/plot-noscat.gp
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170412-self_interaction_potentials_M12_M12-LS220-M1/Run03/RunBA/RunBA-025deg-noscat/flavor_evolution
  \caption{Neutrino survival probabilities for the \emph{noscat} case.
    In the lower panel we reproduce the self-interaction potential $V_{\nu\nu,0}$
    and matter potential $V_e$ from Fig.~\ref{fig:V_nunu-noscat}.
    In this case, the neutrinos undergo collective neutrino oscillation
    beginning around $r\sim700$~km,
    with both the electron neutrinos and antineutrinos almost converting to mu
    or tau neutrinos completely.
  }
  \label{fig:survival-noscat}
\end{figure}

\begin{figure}
  \resizebox{\columnwidth}{!}{\input{fig-survival_prob-scat_ih.tex}}
  % Flavor evolution by Yonglin, see emails 5.9.18, 5.16.18
  % Data: $DIR/300-1499kmACC12Step2NE30IH051418m12sc.dat2p
  % Script: $DIR/plot-scat.gp
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170412-self_interaction_potentials_M12_M12-LS220-M1/Run03/RunBA/RunBA-025deg-scat/flavor_evolution
  \caption{Same as Fig.~\ref{fig:survival-noscat},
    but for the \emph{scat} case.
    In this case the neutrinos undergo a standard MNR transition
    beginning around $r\sim400$~km,
    with the electron neutrinos converting to mu or tau neutrinos almost
    completely,
    and the electron antineutrinos oscillating back to their original flavor
    after partially converting to mu and tau antineutrinos.
  }
  \label{fig:survival-scat}
\end{figure}

>>>>

We also solve for the flavor evolution of this system,
integrating $S$ according to Eqn.~\ref{eqn:schroedinger},
as described in \cite{zhu2016-mnr_nsns_remnant}.
We show the survival probabilities for $\nu_e$ and $\bar{\nu}_e$
in Figs.~\ref{fig:survival-noscat} and \ref{fig:survival-scat},
comparing the \emph{noscat} and \emph{scat} treatments.
In these figures we also show the evolved self-interaction potential
$V_{\rm osc}$,
\begin{equation}
  \label{eqn:V_osc}
  V_{\rm osc} \equiv (H_{\nu\nu})_{ee}-{\rm Tr}(H_{\nu\nu})/3,
\end{equation}
to show how the neutrino interactions driving the oscillation evolve with flavor.
Note that $V_{\rm osc}$ is identical to $V_{\nu\nu,0}$ if no flavor
evolution takes place.
The survival probability is the probability that a neutrino, if measured,
will be found to be in its original flavor state.
The survival probabilities are computed at each point along the trajectory
from the absolute square of the diagonal terms of the flavor evolution matrix,
$P_{\nu_\alpha \to \nu_\alpha} = |S_{\alpha \alpha}|^2$.
When $P_{\nu_e \to \nu_e}$ decreases,
as can be seen for example in Fig.~\ref{fig:survival-scat} for $r>400$~km,
some of the $e$ neutrinos have oscillated into $\mu$ or $\tau$ neutrinos.

@@

\begin{figure}
  \resizebox{\columnwidth}{!}{\input{fig-survival_prob-noscat_ih.tex}}
  % Flavor evolution by Yonglin, see emails 5.9.18, 5.16.18
  % Data: $DIR/300-1499kmACC12Step2NE30IH051418m12sc.dat2p
  % Script: $DIR/plot-noscat.gp
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170412-self_interaction_potentials_M12_M12-LS220-M1/Run03/RunBA/RunBA-025deg-noscat/flavor_evolution
  \caption{Neutrino survival probabilities for the \emph{noscat} case.
    In the lower panel we show the matter potential $V_e$ from
    Fig.~\ref{fig:V_nunu-noscat},
    and the evolved self-interaction potential $V_{\rm osc}$ from
    Eqn.~\ref{eqn:V_osc}.
    In this case, the neutrinos undergo collective neutrino oscillation
    beginning around $r\sim700$~km,
    with both the electron neutrinos and antineutrinos converting to
    heavy-lepton neutrinos and antineutrinos almost completely.
  }
  \label{fig:survival-noscat}
\end{figure}

\begin{figure}
  \resizebox{\columnwidth}{!}{\input{fig-survival_prob-scat_ih.tex}}
  % Flavor evolution by Yonglin, see emails 5.9.18, 5.16.18
  % Data: $DIR/300-1499kmACC12Step2NE30IH051418m12sc.dat2p
  % Script: $DIR/plot-scat.gp
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170412-self_interaction_potentials_M12_M12-LS220-M1/Run03/RunBA/RunBA-025deg-scat/flavor_evolution
  \caption{Same as Fig.~\ref{fig:survival-noscat},
    but for the \emph{scat} case.
    In this case the neutrinos undergo a standard MNR transition
    beginning around $r\sim400$~km,
    with the electron neutrinos converting to heavy-lepton neutrinos almost
    completely,
    and the electron antineutrinos oscillating back to their original flavor
    after partially converting to heavy-lepton antineutrinos.
  }
  \label{fig:survival-scat}
\end{figure}
